A self-consistency check for unitary propagation of Hawking quanta

### 2016-12-05 Draft_BH_shells.tex
discssion
improving the discussion about uncertainty principle

While formulating the information paradox, it is customary to take the large black hole limit.
Such a limit allows us to identify near-horizon modes with wavelength much shorter than the curvature scale, but much longer than the UV cut-off scale.
For these modes, we are confident that they start in local vacuum states of QFT as if they live in Minkowski space.
This large black hole limit, which is effectively a near-Minkowski limit of a near horizon region, is the key argument to eliminate many na\"ive solutions to the information paradox.

The main result in this paper shows that there is a competing effect which stops us from taking this convenient limit.
The geometric uncertainty at distance $l$ from the horizon will only affect near-horizon modes of wavelength shorter than $l$.
If we fix the wavelength of the relevant near-horizon modes and increase the black hole size, our result shows that the unitary propagation to asymptotic Hawking radiation becomes less and less trustworthy. 
Since the dimensionless ratio $(l/M)$ is the only relevant physical parameter that comes into the scaling both effects, there seems to be no middle-ground that can make both unitarity and local-Minkowski-ness arbitrarily reliable.
We think such competition is a good sign and will take us closer to the solution of information paradox.

>>>>

While formulating the information paradox, it is customary to take the large black hole limit.
Technically, it means that we first select a fixed length scale $l$ that is much longer than the UV-cutoff scale of the theory, and study a near-horizon region of this size.
Such a region will be almost identical to a region of the same size in global Minkowski space, since all locally measurable curvature effect is suppressed by $(l/M)$.
If we make the black hole arbitrarily large, $(l/M)$ goes to zero, the for all the field theory modes within this region, we are confident that they start in local vacuum states of QFT as if they live in Minkowski space.
This large black hole limit is the key argument to eliminate many na\"ive solutions to the information paradox.

The main result in this paper shows that there is a competing effect which stops us from taking this convenient limit.
In order for field theory modes from the above region to propagate out and become asymptotic quanta, they must go through geometric uncertainties, like the double-shells in our example, at the distance scale $l$ from the horizon.
If we again fix $l$ and increase $M$, our result in Eq.~(\ref{fin-result}) shows that the unitary propagation to asymptotic Hawking quanta becomes less and less trustworthy. 
Since the dimensionless ratio $(l/M)$ is the only relevant physical parameter that comes into the scaling both effects, there seems to be no middle-ground that can make both unitarity and local-Minkowski-ness arbitrarily reliable.
We think such competition is a good sign and will take us closer to the solution of information paradox.
